Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/structureScene.tex
paper -> article

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The emerging field of computational ecoacoustics aims at retrieving high-level information from the acoustic scenes recorded by some network of sensors.
In this paper, we address the problem of acoustic scene classification (ASC) according to the taxonomy of the DCASE 2013 challenge, both in supervised and unsupervised settings.
Traditional approaches compute a "bag-of-frames", i.e. the summary statistics of short-term audio descriptors, such as mel-frequency cepstral coefficients (MFCCs).
Although they successfully characterize static scenes with little variability in auditory content, they are unable to accurately discriminate scenes with few salient events superimposed over a textured background.
To overcome this issue, we propose a two-scale representation which describes a signal at a short scale using scattering transforms while relying on a cluster model to characterize its larger-scale structure.
We validate the use of the scattering transform for supervised acoustic scene classification by reporting a better accuracy than MFCCs when using a support vector machine (SVM) classifier.
Furthermore, we illustrate the power of the full cluster-based representation by applying it to an acoustic scene similarity retrieval (ASSR) unsupervised task, where we significantly outperform more traditional approaches based on summary statistics of MFCCs.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The emerging field of computational ecoacoustics aims at retrieving high-level information from the acoustic scenes recorded by some network of sensors.
In this article, we address the problem of acoustic scene classification (ASC) according to the taxonomy of the DCASE 2013 challenge, both in supervised and unsupervised settings.
Traditional approaches compute a "bag-of-frames", i.e. the summary statistics of short-term audio descriptors, such as mel-frequency cepstral coefficients (MFCCs).
Although they successfully characterize static scenes with little variability in auditory content, they are unable to accurately discriminate scenes with few salient events superimposed over a textured background.
To overcome this issue, we propose a two-scale representation which describes a signal at a short scale using scattering transforms while relying on a cluster model to characterize its larger-scale structure.
We validate the use of the scattering transform for supervised acoustic scene classification by reporting a better accuracy than MFCCs when using a support vector machine (SVM) classifier.
Furthermore, we illustrate the power of the full cluster-based representation by applying it to an acoustic scene similarity retrieval (ASSR) unsupervised task, where we significantly outperform more traditional approaches based on summary statistics of MFCCs.
\end{abstract}
